---
title       : Twitter Analytics - Sentiment Analysis and more
subtitle    : Developing a shiny application
author      : Karam
job         : Business Intelligence
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## Mining Twitter
Getting a developer Twitter account and curl Certification
```{r , eval=FALSE}
library(twitteR)
library(ROAuth)
library(RCurl)
download.file(url="http://curl.haxx.se/ca/cacert.pem",destfile="cacert.pem")
```
Setting the Certification at Twitter
```{r,eval=FALSE}
# Set constant requestURL
requestURL <- "https://api.twitter.com/oauth/request_token"
# Set constant accessURL
accessURL <- "https://api.twitter.com/oauth/access_token"
# Set constant authURL
authURL <- "https://api.twitter.com/oauth/authorize"
consumerKey <- "xxxxxxxxxxxxxxx"
consumerSecret <- "xxxxxxxxxxxx"
```

--- .class #id 
## Mining Twitter

##### Saving and using the Certification to connect to Twitter

```{r,eval=FALSE}

twitCred <- OAuthFactory$new(consumerKey=consumerKey,
                             consumerSecret=consumerSecret,
                             requestURL=requestURL,
                             accessURL=accessURL,
                             authURL=authURL)
twitCred$handshake(cainfo="cacert.pem")
registerTwitterOAuth(twitCred)
s <- searchTwitter('#wc2014', cainfo="cacert.pem", n=5, locale = 'en', 
                   geocode = '42.375,-71.1061111,10mi')
s
#[[1]]
#[1] "UnitedPlanet: Here’s what you may have missed this past
#weekend and what you may not have known about the FIFA World Cup.
#http://t.co/lmRVlSWnca #WC2014"

```

--- .class #id 
## Developing a shiny product

### Install the `shinyapps` package using `devtools`:
```{r,eval=FALSE}
devtools::install_github('rstudio/shinyapps')
library(shinyapps)
```

In this example, we have placed two Shiny source files: `ui.R` and `server.R`

You can get `ui.R` and `server.R` from my github account [here](https://github.com/Karamcse/shinyapp). 

### Test your Application
```{r,eval=FALSE}
library(shiny)
runApp()

```

--- .class #id 
## Deploy a shiny product
### Configuring ShinyApps
1) To use the shinyapps package, you will need to signup for a ShinyApps account.

2) Configuring your account

3) You will need to retrieve your token from the ShinyApps dashboard. Tokens are listed under the Tokens page found in the menu on the top right of the ShinyApps dashboard.

### Deploy a shiny product

```{r,eval=FALSE}
shinyapps::setAccountInfo(name="<ACCOUNT>", token="<TOKEN>", secret="<SECRET>")
deployApp()

```
Once the deploy finishes, your browser should automatically open up to your newly deployed application.

`My application is` [here](http://karamcse.shinyapps.io/twitteranalysis/)
